jk test with unbalanced label

### 2016-10-18 Rmd/convergenceRatesImbalancedSmallSigma.Rmd
update large and small overlap
bug fixed; moved Rmd out of R package

sigma<-  sqrt(1.7661/10)

@@

  sigma<-  sqrt(1.7661/10)

@@

  jk12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jk22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T)
  jGMM12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)
  jGMM22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F)

@@

if(FALSE)
{

@@

  save(result, file="resultRatesImbalancedLargeSigma.Rda")
}

@@

load("resultRatesImbalancedLargeSigma.Rda")

>>>>

sigma<-  sqrt(1.7661/10000)

@@

  sigma<-  sqrt(1.7661/30)

@@

  jk12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)
  jk22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = T,sigma2_ini = sigma^2)
  jGMM12 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 1,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^2)
  jGMM22 <- jkmeans::jkmeansEMBatch(yBatch, k=2, j = 2,  1000,tol = 1E-10,useKmeansIni = F, meansIni = mu_ini, fixW = F,sigma2_ini = sigma^2)

@@

# if(FALSE)
{

@@

  save(result, file="resultRatesImbalancedSmallSigma.Rda")
}

@@

load("resultRatesImbalancedSmallSigma.Rda")
